---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/congressbr)](https://cran.r-project.org/package=congressbr) [![Travis-CI Build Status](https://travis-ci.org/RobertMyles/congressbr.svg?branch=master)](https://travis-ci.org/RobertMyles/congressbr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/RobertMyles/congressbr?branch=master&svg=true)](https://ci.appveyor.com/project/RobertMyles/congressbr)
[![CRAN_Download_Badge](http://cranlogs.r-pkg.org/badges/congressbr)](https://CRAN.R-project.org/package=congressbr)
[![CRAN_Download_Badge](http://cranlogs.r-pkg.org/badges/grand-total/congressbr)](https://CRAN.R-project.org/package=congressbr)  

## `r emo::ji("brazil")` congressbr

congressbr is a package for extracting data from the APIs of the Brazilian Federal Senate and Chamber of Deputies, respectively. We would like to include lower-level houses in future, if possible.

### Installation

congressbr is on CRAN, and so can be installed with the following:

```{r, eval = F}
install.packages("congressbr")
```

Development versions can be installed with the devtools package: 

```{r, eval = F}
devtools::install_github("RobertMyles/congressbr")
```

### Function naming

We follow [googlesheets](https://github.com/jennybc/googlesheets) in using a naming convention for functions that facilitates tab completion. All Senate-related functions start with `sen_` and all Chamber-related ones start with `cham_`. 

### Principal functions  

- `cham_votes()`: returns voting information from the Chamber of Deputies. 
- `cham_bills()`: returns bill information from the Chamber of Deputies.
- `sen_votes()`: returns voting information from the Federal Senate. 
- `sen_bill_search()`: search for legislature in the Senate.

### Vignettes  

You can learn more about the package with the vignettes. Run `vignette("Exploring the Brazilian Federal Senate")` to download and explore data from the Federal Senate, and `vignette("Exploring the Brazilian Chamber of Deputies")` to do the same for the Chamber of Deputies. 

### Datasets
`congressbr` comes with some pre-prepared datasets.   

- `data("commissions")` returns a dataframe of commissions, with two columns, the full name of the commission, and the abbreviations used in some of the other functions in `congressbr` and in much of the literature on the insitution. 

- `data("senate_nominal_votes")` is a dataframe of all the nominal votes in the Senate between 1991 and early 2017 (the Senate API only allows requests for a maximum period of 60 days).

### Contributions

If you would like to get involved, feel free to fork the repo. We've been using the [Udacity Git Commit Message Style Guide](https://udacity.github.io/git-styleguide/) (well, not *always*). There are a list of open [issues](https://github.com/RobertMyles/congressbr/issues), which is a good place to start. The API of the Federal Senate is also under development, and so elements of this package may change. If you find any problems with the package, please open an issue and leave us a reproducible example and we'll get it fixed asap. 

## List of functions  

For convenience, we list here the functions of the package. More details are available [here](https://cran.r-project.org/web/packages/congressbr/congressbr.pdf). 

- `cham_bills`: Downloads and tidies data for lists of bills in Brazilian Chamber of Deputies. 
- `cham_bill_info`: Downloads details of a specific bill by providing type, number and year.  
- `cham_bill_info_id`: Downloads details of a specific bill by providing id of a bill.
- `cham_plenary_bills`: This function lists every bill voted on in the plenary.
- `cham_typeauthors_bills`: Types of authors for bills.
- `cham_votes`: Downloads votes of a specific bill by providing type, number and year. A bill can have more than one roll call, and the API does not provide an id to identify them So we provide one (rollcall_id).  
- `sen_agenda`: Returns info on the agenda in the Federal Senate.
- `sen_bills`: Information on the legislation in the Federal Senate.
- `sen_bills_current`: Downloads and tidies information on legislation from the *current* legislature of the Federal Senate.
- `sen_bills_limits`: Downloads and tidies information on the types of deadline and time limits for legislation in the Federal Senate.
- `sen_bills_list`: Information on the types of acts that can be formally made in the Federal Senate.
- `sen_bills_locations`: Downloads and tidies information on the possible locations a piece of legislation can currently be passing through the Federal Senate.
- `sen_bills_passage`: Downloads and tidies information on the locations a piece of legislation is currently passing through.
- `sen_bills_passing`: Downloads and tidies information on legislation that is currently under consideration in the Senate.
- `sen_bills_situations`: Possible situations a bill can be in.
- `sen_bills_topics`: Downloads and tidies information on the topics of legislation in the Federal Senate.
- `sen_bills_types`: Information on the types of legislation in the Senate.
- `sen_bills_updates`: Info on bills that have been recently updated.
- `sen_bills_update_types`: Information on the types of updates that can be applied to bills in the Federal Senate.
- `sen_bill_search`: Search for data on legislation in the Brazilian Federal Senate.
- `sen_bill_sponsors`: Bill sponsors in the Senate.
- `sen_budget`: Downloads and tidies budget information from the Federal Senate.
- `sen_coalitions`: Downloads and tidies data on the coalitions in the Federal Senate
- `sen_coalition_info`: Downloads and tidies data on *specific* coalitions in the Federal Senate.
- `sen_commissions`: Information on commissions in the Senate.
- `sen_commissions_senators`: Information on the senators who serve on a certain commission in the Federal Senate.
- `sen_commissions_type`: Information on commissions in the Federal Senate, by commission type.
- `sen_commission_positions`: Information on positions (jobs) that legislators may occupy in commissions in the Federal Senate
- `sen_parties`: Downloads and tidies information on the political parties in the Federal Senate.
- `sen_plenary_agenda`: Returns results from the plenary in the Federal Senate for a specified date.
- `sen_plenary_leaderships`: Returns information on leaderships in the Federal Senate.
- `sen_plenary_result`: Returns results from the plenary in the Federal Senate for a specified date.
- `sen_plenary_sessions`: Returns the types of sessions in the Federal Senate.
- `sen_senator`: Downloads and tidies personal information on senators. Includes absences and mandates.
- `sen_senator_bills`: Downloads and tidies information on bills that certain senators have sponsored/authored in the Senate.
- `sen_senator_commissions`: Downloads and tidies information on the commissions on which senators have served or are serving in the Federal Senate.
- `sen_senator_details`: Downloads and tidies personal information on the senators.
- `sen_senator_legis`: Downloads and tidies information on the senators, by legislature.
- `sen_senator_list`: Returns a list of senators.
- `sen_senator_mandates`: Downloads and tidies information on senators’ mandates.
- `sen_senator_suplentes`: Downloads and tidies information on titular senators and their *suplentes*.
- `sen_senator_votes`: Returns information on senators’ voting histories.
- `sen_sponsor_types`: Types of bill sponsors.
- `sen_statement_list`: Types of declarations senators can make.
- `sen_votes`: Returns voting information from the Senate floor for the date requested.
- `statesBR`: A dataframe of Brazilian states, by their sigla (acronym) and full name.
- `UF`: This function prints out a character vector of Brazilian state abbreviations to the console. 
