---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/congressbr)](https://cran.r-project.org/package=congressbr) [![Travis-CI Build Status](https://travis-ci.org/RobertMyles/congressbr.svg?branch=master)](https://travis-ci.org/RobertMyles/congressbr) [![Coverage Status](https://img.shields.io/codecov/c/github/RobertMyles/congressbr/master.svg)](https://codecov.io/github/RobertMyles/congressbr?branch=master)  

## congressbr

congressbr is a package for extracting data from the APIs of the Brazilian Federal Senate and Chamber of Deputies, respectively (and perhaps lower level congresses eventually, if we can). 

### installation

As of yet, congressbr is not on CRAN. It can be installed with the devtools package: 

```{r, eval = F}

devtools::install_github("RobertMyles/congressbr")

```

### function naming

We follow [googlesheets](https://github.com/jennybc/googlesheets) in using a naming convention for functions that facilitates tab completion. All Senate-related functions start with `sen_` and all Chamber-related ones start with `cam_` ('Câmara'). 

### principal functions  

- `sen_votes()`: returns voting information from the Federal Senate. 
- `sen_bill_search()`: search for legislature in the Senate.


### contributions

If you want to help us, feel free to fork the repo. We've been using the "Udacity Git Commit Message Style Guide" (https://udacity.github.io/git-styleguide/). There are a list of open [issues](https://github.com/RobertMyles/congressbr/issues), which is a good place to start. 
  
This package is under development and so contributions are welcome. The API of the Federal Senate is also under development, and so elements of this package may change. 
