---
title: "Exploring the Brazilian Chamber of Deputies"
author: "Robert McDonnell and Danilo Freire"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring the Brazilian Chamber of Deputies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`congressbr` makes it easy to explore the API of the Brazilian _Câmara dos Deputados_, or the Chamber of Deputies. The package contains many functions that help scholars to download, standardise and tidy data from the _Câmara_ website. This vignette shows some examples.

First, we need to install `congressbr`. You can install the package by running: 
```{r, eval = F}
if(!require(devtools)){install.packages("devtools")}
devtools::install_github("RobertMyles/congressbr")
library(congressbr)
```
```{r, echo=F, message=F, warning=F}
library(congressbr)
```

##Votes

`congressbr` has a dedicated function that returns a dataset with information about votes of a specific bill in the _Câmara dos Deputados_, the `cam_get_votes()` function. As we mentioned in the [Senate vignette](senate.html), the votes returned by the API are not necessarily *nominal* votes. This is because some votes are secret, thus the API only informs us if the deputy voted or not. Users have to provide the type (`type =`), number (`number =`) and year (`year =`) of the bill in question. Unfortunately, a particular bill can have more than one roll call, and the API does not provide an id to identify them. So we have provided one, the variable `id_rollcall` in the data frame. For instance, we can retrieve information about the proposition 1992/2007 with:

```{r}
cam_get_votes(type="PL", number="1992", year="2007")
```

The function returns many values that may be interesting to users, such as the summary of the decision (`summary_decision`), the guidelines given by the government and the opposition to the members of their respective coalitions (`orient_GOV` and `orient_Minoria`) and what political parties suggested to their deputies. In the example above, we could see how the PSDB (`orient_PSDB`) and the PSOL (`orient_PSOL`) orientated their members. 

We can also get information about the legislator who proposed the bill, such as his or her name (`name_legislator`), the state that he or she represents (`uf_legislator`), and his or her party affiliation (`party_legislator`). Those variables are available for each voting stage of the bill. 

##Bills

We have included two functions that retrieve details about particular bills. The first of them is `cam_bill_info()`; the function requires the id of the bill. As an example, we can download some information about a [proposal for constitutional amendment by Espiridião Amin](http://www.camara.gov.br/proposicoesWeb/fichadetramitacao?idProposicao=14784), which has the id 14784, using the code below:


```{r}
cam_bill_info(14784)
```

Another way of downloading the same information would be to use the `cam_bill_info_tny()` function. This function requires three parameters, the bill's type (`type =`), number (`number =`) and year (`year =`). To retrieve the above-mentioned proposal (_projeto de emenda constitucional_), the PEC 472/1997, you can type:

```{r}
cam_bill_info_tny(type="PEC", number="472", year="1997")
```

In another example, we can download data about the law proposition (_projeto de lei_) 3892/2008 with:

```{r}
cam_bill_info_tny(type="PL", number="3962", year="2008")
```

The functions return 19 variables, including the decision situation of the proposition (`desc_situation`), the full text in pdf (`link_complete`), and personal information about the author of the proposition (`name_author`, `abrstate_author`, and `party_author`).

Users can download all every bill voted on in plenary in a given calendar year with `cam_plenary_bills()`. The function has a single parameter, `year = `, and returns the id of the bill (`id_bill`), its name (`name_bill`), and the day on which it was voted (`date_voted`)

```{r}
cam_plenary_bills(year=2008)
```

Finally, `congressbr` also features `cam_typeauthors_bills()`, a convenience function that downloads the types of authors for bills.

```{r}
cam_typeauthors_bills()
```

##Examples

In this brief example, we will examine how the parties orientated their deputies to vote in the law proposition 1992/2007, the same we have downloaded with the `cam_get_votes()` function. This example makes use of the `ggplot2` package.

```{r}
if(!require(ggplot2)){install.packages("ggplot2")}
library(ggplot2)

party_orientation <- cam_get_votes(type="PL", number="1992", year="2007")
party_orientation <- as.data.frame(t(party_orientation[1, c(7, 10:22)])) # select only one row and the columns of interest; transpose data
names(party_orientation)[1] <- "orientation"

ggplot(party_orientation, aes(x = orientation)) +
  geom_bar(aes(fill = orientation), colour = "white") +
  theme_classic() + 
  scale_fill_hue(l=40) + 
  ggtitle("Party Orientation - PL 1992/2007") +
  labs(x="Orientation", y="Count") + 
  theme(legend.position="none")
```

Similarly, we could also have used the `dplyr` package to see how many parties suggested their members to vote "yay" (_sim_), "nay" ("não"), or allowed deputies to decide their votes (_liberado_).

```{r}
if(!require(dplyr)){install.packages("dplyr")}
library(dplyr)

party_orientation %>%
  group_by(orientation) %>%
  tally()
```


