---
title: "Exploring the Brazilian Chamber of Deputies"
author: "Robert McDonnell, Guilherme Duarte and Danilo Freire"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring the Brazilian Chamber of Deputies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`congressbr` makes it easy to explore the API of the Brazilian Chamber of Deputies, or the _Câmara dos Deputados_. The package contains many functions that help researchers to download, standardise and tidy data from the _Câmara_ website. This vignette shows some examples.

First, we need to install `congressbr`. You can install the package by running: 
```{r, message = F, warning=F}
if(!require(devtools)){install.packages("devtools", repos = "http://cran.us.r-project.org")}
devtools::install_github("RobertMyles/congressbr")
library(congressbr)
```


## Votes

`congressbr` has a dedicated function that returns a dataset with information about votes of a specific bill in the _Câmara dos Deputados_, the `cham_votes()` function. As we mentioned in the [Senate vignette](senate.html), the votes returned by the API are not necessarily *nominal* votes. This is because some votes are secret, thus the API only informs us if the deputy voted or not. Users have to provide the type (`type =`), number (`number =`) and year (`year =`) of the bill in question. Unfortunately, a particular bill can have more than one roll call, and the API does not provide an id to identify them. So we have provided one, the variable `rollcall_id` in the data frame. For instance, we can retrieve information about the proposition 1992/2007 with:

```{r}
cham_votes(type = "PL", number = "1992", year = "2007")
```

The function returns many values that may be interesting to users, such as the summary of the decision (`decision_summary`), the guidelines given by the government and the opposition to the members of their respective coalitions (`GOV_orientation` and `Minoria_orientation`) and what political parties suggested to their deputies. In the example above, we could see how the PSDB (`PSDB_orientation`) and the PSOL (`PSOL_orientation`) orientated their members. 

We can also get information about the legislator who proposed the bill, such as his or her name (`legislator_name`), the state that he or she represents (`legislator_state`), and his or her party affiliation (`legislator_party`). Those variables are available for each voting stage of the bill. 

## Bills

We have included two functions that retrieve details about particular bills. The first of them is `cham_bill_info()` function. This function requires three parameters, the bill's type (`type =`), number (`number =`) and year (`year =`). To retrieve the above-mentioned proposal (_projeto de emenda constitucional_), the PEC 472/1997, you can type:

```{r}
cham_bill_info(type = "PEC", number = "472", year = "1997")
```

In another example, we can download data about the law proposition (*projeto de lei*) 3892/2008 with:

```{r}
cham_bill_info(type = "PL", number = "3962", year = "2008")
```

The function return 19 variables, including the decision situation of the proposition (`situation_desc`), the full text in pdf (`complete_link`), and personal information about the author of the proposition (`author_name`, `author_state`, and `author_party`).

Another way of downloading the same information would be to use `cham_bill_info_id()`. The function requires the id of the bill. As an example, we can download some information about a [proposal for constitutional amendment by Espiridião Amin](http://www.camara.gov.br/proposicoesWeb/fichadetramitacao?idProposicao=14784), which has the id 14784, using the code below:

```{r}
cham_bill_info_id(14784)
```

Users can download all every bill voted on in plenary in a given calendar year with `cham_plenary_bills()`. The function has a single parameter, `year = `, and returns the id of the bill (`bill_id`), its name (`bill_name`), and the day on which it was voted (`vote_date`)

```{r}
cham_plenary_bills(year = 2008)
```

Finally, `congressbr` also features `cham_typeauthors_bills()`, a convenience function that downloads the types of authors for bills.

```{r}
cham_typeauthors_bills()
```

## Examples

In this brief example, we will examine how the parties orientated their deputies to vote in the law proposition 1992/2007, the same we have downloaded with the `cham_votes()` function. This example makes use of the `ggplot2` package.

```{r, message = F, warning = F}
if(!require(ggplot2)){install.packages("ggplot2", repos = "http://cran.us.r-project.org")}
library(ggplot2)

party_orientation <- cham_votes(type = "PL", number = "1992", year = "2007")
party_orientation <- as.data.frame(t(party_orientation[1, c(7, 10:22)])) # select only one row and the columns of interest; transpose data
names(party_orientation)[1] <- "orientation"

ggplot(party_orientation, aes(x = orientation)) +
  geom_bar(aes(fill = orientation), colour = "white") +
  theme_classic() + 
  scale_fill_hue(l = 40) + 
  ggtitle("Party Orientation - PL 1992/2007") +
  labs(x = "Orientation", y = "Count") + 
  theme(legend.position = "none")
```

Similarly, we could also have used the `dplyr` package to see how many parties suggested their members to vote "yay" (*sim*), "nay" (*não*), or allowed deputies to decide their votes (*liberado*).

```{r, message = F, warning = F}
if(!require(dplyr)){install.packages("dplyr", repos = "http://cran.us.r-project.org")}
library(dplyr)

party_orientation %>%
  group_by(orientation) %>%
  tally()
```


